Molecular transport in human pial perivasculature

### 2024-11-11 paper/cut.tex
Just commit changes
Former-commit-id: b0716566f8c908e3bf54eb6f60b870a3e40dabcb
More shuffling in Methods. Short snippets targeting general audience in Methods; complete version targeting math readers in the Supplementary Methods.

>>>>

We consider non-zero convection in the CSF space $u_{\rm CSF} \not = 0$ in \eqref{eq:multi_transport_3d} resulting from steady state CSF production.  Recall that $\Omega_{\mathrm{CSF}}$ represents the CSF space and that $\Gamma_{\mathrm{skull^{u/l}}}$ and $\Gamma_{\mathrm{pia}}$, $\Gamma_{\mathrm{LV}}$ represent the boundaries facing the upper and lower parts of the dura, the pia and the lateral ventricles, respectively.  Assuming CSF production in the choroid plexus located at the lateral ventricle wall, we solve the  steady state Stokes equations for the velocity and the pressure $(\bm u_{\mathrm{CSF}}, p_{\mathrm{CSF}})$ in the CSF domain: 
\begin{subequations}
    \begin{alignat}{2}
 - \mu \Delta \bm u_{\mathrm{CSF}} + \nabla p_{\rm{CSF}} & =  0 \quad && \mathrm{in} \,\,  \Omega_{\rm CSF}, \label{eq:momnetum_equation}  \\ 
 \nabla \cdot  \bm u_{\mathrm{CSF}} & = 0 \quad && \mathrm{in} \,\,   \Omega_{\rm CSF}, \label{eq:divergence_equation}  \\ 
\mu \nabla \bm u_{\mathrm{CSF}} \cdot \bm{n} -  p \bm n  &  = -R_0 ( \bm u \cdot \bm n ) \bm n\,\,   && \mathrm{on}  \label{eq:efflux_condition} \,\, \Gamma_{\mathrm{skull^u}}, \\ 
\bm u_{\mathrm{CSF}} & = 0 && \mathrm{on} \,\, \Gamma_{\rm{pia}} \cup \Gamma_{\mathrm{skull^l}} \Gamma_{\rm{SSAS}}  \\
\bm u_{\mathrm{CSF}} \cdot \bm n & = \frac{1}{ |\Gamma_{\rm LV}|}  u_{\rm in}, \quad \bm u \cdot \bm \tau = 0 \quad && \mathrm{on} \,\, \Gamma_{\rm{LV}} .  
\end{alignat}
\end{subequations}

Here, $\bm n$ denotes the unit outward normal to the boundary, $\mu$ is the CSF viscosity, and $\bm u_{\rm in}$ is the steady CSF flow across the lateral ventricle wall, see \Cref{tab:pvs:parameters}.
Condition \eqref{eq:efflux_condition} models an efflux site with positive resistance $R_0 \geq 0$. The Stokes system is solved with the finite element software $FEniCS$, stored and then subsequently read for all the relevant solute transport simulations. See Figure~\ref{fig:csf_flow_cardiac} for a streamline visualization of the obtained velocity profile and \Cref{sec:details_numerical_method} for details on the numerical algorithm employed.

%% \begin{figure}
%%      \centering
%%      \begin{subfigure}[b]{0.45\textwidth}
%%          \centering
%%          \includegraphics[width=\textwidth]{figures/Brain-PVS-callouts.pdf}
%%          \label{fig:intracranial_domains}
%%      \end{subfigure}
%%      \hfill
%%      \begin{subfigure}[b]{0.3\textwidth}
%%          \centering
%%          \includegraphics[width=\textwidth]{figures/geometry_concept.png}
%%          \caption{The arterial (red) and venous (blue) networks (top left), the parenchyma and CSF space (top right), combined (bottom row)}
%%          \label{fig:three sin x}
%%      \end{subfigure}
%%      \hfill
%%      \begin{subfigure}[b]{0.24\textwidth}
%%          \centering
%%          \includegraphics[trim={4cm 0 4cm 0},clip,width=\textwidth]{figures/labeled_arteries.png}
%%          \caption{The arterial network with the main cerebral arteries: internal carotid artery (ICA), middle cerebral artery (MCA), anterior cerebral artery (ACA) and posterior cerebral artery (PCA)}
%%          \label{fig:five over x}
%%      \end{subfigure}
%%      %\caption{@Marius: Starts adding parts of this. \mer{MER: Concept figure illustrating the compartments and story line. (A) Concept sketch of the SAS, PVS and the brain; (B) Visualization of geometry domains (brain, sas and vasculature; think about colors and associations; please don't make blood blue and water red e.g.) ; (C) Zoom-in/detail on vasculature, which are which arteries (ACA, MCA, PCA, CoW)  and veins (XXX); (D) Zoom-in 2 on vascular position versus SAS and brain; (E) Zoom-in 3 on where PVS ends; (F) Illustration of boundaries? (G) Concept illustration of the mathematical model (diffusion, convection, exchange, boundaries).}}
%% \label{fig:concept}
%% \end{figure}
